Supplemental Materials: Polymethylation Scores for Prenatal Maternal Smoke Exposure Persist Until Age 15 and Are Detected in Saliva

### 2022-02-02 Reports/Paper1.Rmd
reviewer comment: 95% CI AUC and 95% CI AUC-differences

```{r supplemental table auc}
roc_table=global_roc %>% dplyr::select(childteen, methylation, modeltype, roc, auc)
roc_base=roc_table %>% filter(modeltype=='Base model+No methylation')%>%mutate(roc_basemodel=roc)%>%dplyr::select(childteen, roc_basemodel)
roc_ss=roc_table %>% filter(modeltype=='Base model+Sustained smoking polymethylation score (newborns, cell-type controlled)')%>%mutate(roc_pms=roc)%>%dplyr::select(childteen, roc_pms)

rct1=roc_table%>% 
  filter(methylation %in% c('globalmethylation', 'cg05575921', 'SSnewbornCT_center_scale', ''))%>%
  left_join(roc_base)%>%
  mutate(roctest_base=map2(roc, roc_basemodel, ~roc.test(.x, .y)))%>%
  left_join(roc_ss)%>%
  mutate(roctest_ss=map2(roc, roc_pms, ~roc.test(.x, .y)))%>%
  mutate(auc=round(auc, 2))%>%
  mutate(`P value vs polymethylation score`=map_dbl(roctest_ss, ~round(.x$p.value, 4)))%>%
  mutate(`P value vs base model`=map_dbl(roctest_base, ~round(.x$p.value, 4)))%>%
  dplyr::select(childteen, modeltype, auc, `P value vs base model`, `P value vs polymethylation score`)

>>>>

```{r supplemental table auc}
#CI.delong is the confidence interval for each auc: if we sampled 100 times, 95 of the samples would have a auc between those two numbers
roc_table=global_roc %>% 
  dplyr::select(childteen, methylation, modeltype, roc, auc, ci_auc_delong, ci_auc_boot)%>%
  mutate(ci.delong=map_chr(ci_auc_delong, ~paste(round(.x[1], 2), round(.x[3], 2), sep=', ')))

roc_base=roc_table %>% 
  filter(modeltype=='Base model+No methylation')%>%
  rename_with(~str_c(., '_basemodel'), .cols=c(roc, auc, ci.delong))%>%
  dplyr::select(childteen, contains('_basemodel'))

roc_ss=roc_table %>% 
  filter(modeltype=='Base model+Sustained smoking polymethylation score (newborns, cell-type controlled)')%>%
  rename_with(~str_c(., '_pms'), .cols=c(roc, auc, ci.delong))%>%
  dplyr::select(childteen, contains('_pms'))

#confidence_interval_difference_pms|base is the confidence interval for the DIFFERENCE between the two aucs - if we took 100 samples of the difference between the aucs, 95 of them would be between those two numbers: avoids incorrect error propagation, since the squares of errors add, not the errors themselves (see an explanation here: https://towardsdatascience.com/why-overlapping-confidence-intervals-mean-nothing-about-statistical-significance-48360559900a)
rct1=roc_table%>% 
  filter(methylation %in% c('globalmethylation', 'cg05575921', 'SSnewbornCT_center_scale', ''))%>%
  left_join(roc_base)%>%
  mutate(roctest_base=map2(roc, roc_basemodel, ~roc.test(.x, .y)))%>%
  left_join(roc_ss)%>%
  mutate(roctest_ss=map2(roc, roc_pms, ~roc.test(.x, .y)))%>%
  mutate(auc=round(auc, 2))%>%
  mutate(`P value vs polymethylation score`=map_dbl(roctest_ss, ~round(.x$p.value, 4)))%>%
  mutate(`P value vs base model`=map_dbl(roctest_base, ~round(.x$p.value, 4)))%>%
  mutate(confidence_interval_difference_base=map_chr(roctest_base, ~paste(round(.x$conf.int[1], 2), round(.x$conf.int[2], 2), sep=', ')))%>%
  mutate(confidence_interval_difference_pms=map_chr(roctest_ss, ~paste(round(.x$conf.int[1], 2), round(.x$conf.int[2], 2), sep=', ')))%>%
  dplyr::select(childteen, modeltype, auc, `P value vs base model`, `P value vs polymethylation score`, confidence_interval_difference_base, confidence_interval_difference_pms)
